**COVID-19 vaccination in Ontario: Exploring intra-provincial variations within Health Regions and socio-economic strata**

### 2023-03-26 manuscript_v2/appendix.qmd
Updated files

We used the iterative proportional fitting procedure (_raking_) in order to account for the differences in income, age groups, race/ethnicity and the population from the Health Regions. Details of the implementation can be found in the R Script `raking_logistic_regression.R` in the `code` directory.

@@

The tables below present summaries of information from the Fields survey (from the clean dataset analyzed in the main paper), showing responses by White/Caucasian individuals by Health Region and proportion of answers by LHIN in the West Health Region.

>>>>

We used the iterative proportional fitting procedure (_raking_) in order to account for the differences in income, age groups, race/ethnicity and the population from the Health Regions. Details of the implementation can be found in the R Script `raking.R` in the `code` directory.

@@

Tables A-7 and A-8 present summaries of information from the Fields survey (from the clean dataset analyzed in the main paper), showing responses by White/Caucasian individuals by Health Region and proportion of answers by LHIN in the West Health Region.
